### 2024-06-18 ms.qmd
Update ms.qmd

All tests were done between 10 and 12 in the morning when the lizards werew most active. Each trial was performed daily for five days, between the 17^th^ to the 22^nd^ of May 2024. After the tests, videos were analysed to record: a) the first choice of the lizard (1 if it was the higher number, 0 if not), b) the latency, or time spent by the lizard to make a choice, c) the time spent close to a choice after five minutes of perceiving it, and d) the number of attacks towards a choice for 5 min after perceiving it. We considered a choice when the lizard touched the Petri dish with its snout, by then, we considered that the choice had been perceived. Finally, we considered an attack when the lizard tried to bite the Petri dish.

>>>>

All tests were done between 10 and 12 in the morning when the lizards werew most active. Each trial was performed daily for five days, between the 17^th^ to the 22^nd^ of May 2024. After the tests, videos were analysed manually using (**PROGRAM**). We recorded two main variables: the first choice of the lizard, and the interest shown for the higher amount of food. The first choice was obtained after the first interaction with one of the two options: 1 if they interacted with the higher number of items first, 0 if not. For us to determine the first choice, we considered that the lizard was interacting with the food when it touched the Petri dish with its snout or when the front half of the body was on top of the platform. For five minutes after the first interaction with each option, we recorded the time spent interacting with it; we did this for both amounts of food independently of what was the first choice. We measured the interest shown for the higher amount of food by substracting the time spent (for a max of 5 min) in the platform with less crickets to the time spent in the platform with more crickets. This gave as a gradient from -300 to +300 where the minimum represents interest in the lower amount of food and the maximum shows a preference towards higher number of crickets, while 0 shows no discrimination between them. If there was no interaction with one of the options during the test, we considered the time spent as 0 for that option. When there was no interaction with any of the choices, both choice and interest were noted as NA. We excluded from the analyses all the individuals that did not participate in less than three of the tests.
